### 2016-06-16 capability-machine.tex
added questions for malloc specification

The ticket dispenser test program uses $\malloc$. To be able to reason about programs that use $\malloc$, we assume that it obeys the following specification. If you provide it with one argument, namely the size of the allocation you wish and a return capability, then at some point $\pcreg$ will contain an executable capability based on this return capability and the return register will contain a $\rwx$ capability for the freshly allocated memory. 
\begin{specification}[Malloc (D)]
Take $W_{\malloc}$ the world with exactly one island, namely the unspecified island $\iota_{\malloc}$ that governs the internal state of $\malloc$.  If we invoke $\malloc$ in a memory $h = \hs_{\var{frame}} \uplus \hs_{\var{footprint}}$ that is the disjoint sum of a frame part and a footprint part and the latter satisfies this world up to steps $n$, i.e., $\heapSat[\hs_{\var{footprint}}]{n}{W_{\malloc}}$. Then $\malloc$ will succesfully terminate and return a result in a heap $h' = \hs_{\var{frame}} \uplus \hs_{\var{footprint}}'$ that is the disjoint sum of the same unmodified frame part and a potentially new footprint part, such that there is a future world $W'$ of $W_{\malloc}$ consisting of exactly two islands, where the first is an instance of $\iota_{\malloc}$ and the second is the region $\iota_{\var{base},\var{end}}$ \lau{doesn't this invariant allow the newly allocated memory to contain capabilities?} for an appropriately-sized interval $\var{base},\var{end}$ and the new footprint part satisfies this new world $\heapSat[\hs_{\var{footprint}}']{?}{W'}$. \lau{at what step should this hold? Just some step n'<n? Also it should probably be more precise what it means to ``invoke'' $\malloc$ and for $\malloc$ to ``return'' something.}
\end{specification}

>>>>

The ticket dispenser test program uses $\malloc$. To be able to reason about programs that use $\malloc$, we assume that it obeys the following specification. If you provide it with one argument, namely the size of the allocation you wish and a return capability, then at some point $\pcreg$ will contain an executable capability based on this return capability and the return register will contain a $\rwx$ capability for the freshly allocated memory. 
\begin{specification}[Malloc (D)]
Take $W_{\malloc}$ the world with exactly one island, namely the unspecified island $\iota_{\malloc}$ that governs the internal state of $\malloc$.  If we invoke $\malloc$ in a memory $h = \hs_{\var{frame}} \uplus \hs_{\var{footprint}}$ \\
\lau{Is $hs_{\var{frame}}$ supposed to be the rest of memory, so $h$ is something we can execute in? Is $\malloc$ allowed to allocate more memory, i.e., how does $\hs_{\var{footprint}}$ relate to $\hs_{\var{footprint}}'$?}\\
that is the disjoint sum of a frame part and a footprint part and the latter satisfies this world up to steps $n$, i.e., $\heapSat[\hs_{\var{footprint}}]{n}{W_{\malloc}}$. Then $\malloc$ will succesfully terminate and return a result in a heap $h' = \hs_{\var{frame}} \uplus \hs_{\var{footprint}}'$ that is the disjoint sum of the same unmodified frame part and a potentially new footprint part, such that there is a future world $W'$ of $W_{\malloc}$ consisting of exactly two islands, where the first is an instance of $\iota_{\malloc}$ and the second is the region $\iota_{\var{base},\var{end}}$\\
\lau{doesn't this invariant allow the newly allocated memory to contain capabilities?}\\
 for an appropriately-sized interval $\var{base},\var{end}$ and the new footprint part satisfies this new world $\heapSat[\hs_{\var{footprint}}']{?}{W'}$. 
\lau{at what step should this hold? Just some step $n'<n$?}\\
\lau{It should probably be more precise what it means to ``invoke'' $\malloc$ and for $\malloc$ to ``return'' something.}\\
\lau{How do we express that $\malloc$ can be ``trusted'' in the sense that it won't save the capab}
\end{specification}
